Predicting Which States are Most Interested in the term *China Virus* Based off Identity Politics, Demography and COVID-19 Statistics 

### 2020-05-04 Final-Draft.Rmd
visuals

# 2. Data
```{r results = "hide", echo=FALSE, warning=FALSE, message = FALSE}

@@

Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
day_initial<- as.Date("2020-03-14")
day_final<- as.Date("2020-03-21")
Finaldata<- Finaldata%>%
  filter(Day>=day_initial)%>%
  filter(Day<=day_final)

names(Finaldata)
```

@@

### 2.3a Demographic 
```{r, warning=FALSE, message= FALSE, echo=FALSE}
#Demographic: Identification 
Finaldata <- data.frame(Finaldata) %>% mutate(state = State)

p1<- plot_usmap(data = Finaldata, values = "percent_white", color = "white") + 
  scale_fill_continuous(name = "Percent White", label = scales::comma) + 
  theme(legend.position = "right")+ ggtitle("Percent of Residents that Identify as White") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_viridis_c(option = "plasma") + theme(plot.title = element_text(size=11))+ labs(fill = "% White")

ggplotly(p1)

p2<- plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
  scale_fill_continuous(name = "Percent Asian", label = scales::comma) + 
  theme(legend.position = "right")+ ggtitle("Percent of Residents that Identify as Asian") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_viridis_c(option = "plasma") + theme(plot.title = element_text(size=11))+ labs(fill = "% Asian")

ggplotly(p2)

@@

```{r, warning=FALSE, message= FALSE, echo=FALSE}
e <- Finaldata%>%
  ggplot(aes(x = ChinaVirusInterest))+
  geom_density()

e
```

@@

As we can see from the density plot of the China Virus Interest during our time period 2020-03-14 - 2020-03-21, it behaves relatively normal with a small bump at 0. As a group we believe this bump occurs as 0 is the lowest value it can take and because of that limitation of the China Virus Interest we see a small bump around 0. One could argue against a normal distribution as it kinda looks a bit right skewed. But our team believes that a normal distribution is the best at describing the density.

When China Virus Interest equals 0 it means that no one in the state looked up the term in Google and this is prevalent at the 14 of March where there are 5 occurrences and the 21 of March where there are 4 occurrences. And in states such as DC, ND, SD, and VT.

@@

ggplotly(a)
```
This plot shows the relationship of “China Virus” search interest over grouped by region. This plots shows that there are certainly key events that trigger an uptick in searches overall. In this plot it is not clear which region may search China Virus more or less often, but it does show a that the regions move together in search interest, which would imply federal level events like a Donald Trump tweet to trigger these interest spikes.

```{r, warning=FALSE, message= FALSE, echo=FALSE}
b<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State")

ggplotly(b)
```

>>>>

# 2. Data
```{r, message=FALSE, include=FALSE}

@@

Finaldata <- Finaldata %>% mutate(Day= as.Date(Day, tryFormats = "%m/%d/%Y"))

day_initial<- as.Date("03/14/2020",tryFormats = "%m/%d/%Y")
day_final<- as.Date("03/21/2020",tryFormats = "%m/%d/%Y")

Finaldata<- Finaldata%>%
  filter(Day>=day_initial)%>%
  filter(Day<=day_final)

@@

### 2.3a Demographic

```{r}
Finaldata$hover <- with(Finaldata, paste(polyname, "<br>","Positive Cases:", positive, "<br>","Negative Cases:", negative,"<br>",
                           "Total Cases:", totalTestResults,"<br>", "% White:", percent_white,"<br>",
                            "% Asian:", percent_asian, "<br>", "State Color:", StateColor,
                        "<br>", "Total Population", total_population))
# give state boundaries a white border
l <- list(color = toRGB("white"), width = 2)
# specify some map projection/options
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

fig <- plot_geo(Finaldata, locationmode = 'USA-states')
fig <- fig %>% add_trace(
    z = ~ChinaVirusInterest, text = ~hover, locations = ~State,
    color = ~ChinaVirusInterest, colors = 'Oranges'
  )
fig <- fig %>% colorbar(title = "Interest")
fig <- fig %>% layout(
    title = '2020 Google Search Interest of "China Virus" by State <br>(Hover for additional information)', geo=g
  )

fig
```
```{r}
Finaldata$hover <- with(Finaldata, paste(polyname, "<br>","Positive Cases:", positive, "<br>","Negative Cases:", negative,"<br>",
                           "Total Cases:", totalTestResults,"<br>", "% White:", percent_white,"<br>",
                            "% Asian:", percent_asian, "<br>", "State Color:", StateColor,
                        "<br>", "Total Population", total_population))
# give state boundaries a white border
l <- list(color = toRGB("white"), width = 2)
# specify some map projection/options
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

fig <- plot_geo(Finaldata, locationmode = 'USA-states')
fig <- fig %>% add_trace(
    z = ~percent_white, text = ~hover, locations = ~State,
    color = ~percent_white, colors = 'Blues'
  )
fig <- fig %>% colorbar(title = "Interest")
fig <- fig %>% layout(
    title = '2020 Percent White by State <br>(Hover for additional information)', geo=g
  )

fig
```
```{r}

@@

@@

@@

ggplotly(a)
```

This plot shows the relationship of “China Virus” search interest over grouped by region. This plots shows that there are certainly key events that trigger an uptick in searches overall. In this plot it is not clear which region may search China Virus more or less often, but it does show a that the regions move together in search interest, which would imply federal level events like a Donald Trump tweet to trigger these interest spikes.

```{r, warning=FALSE, message= FALSE, echo=FALSE}
b<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State") + labs(fill="State")

ggplotly(b)
```
As we can see from the density plot of the China Virus Interest during our time period 2020-03-14 - 2020-03-21, it behaves relatively normal with a small bump at 0. As a group we believe this bump occurs as 0 is the lowest value it can take and because of that limitation of the China Virus Interest we see a small bump around 0. One could argue against a normal distribution as it kinda looks a bit right skewed. But our team believes that a normal distribution is the best at describing the density.
